---
title: "KRSA Manuscript"
author: "Khaled Alganem"
date: "3/7/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(KRSA)
library(knitr)
library(tidyverse)

library(gt) # can be used to view tables
library(furrr)
```

## Reading Data


```{r readData, include=FALSE, cache=TRUE}

# Define chip type
chipType <- "STK"

# Read crosstab view bionavigator files and tidy data
data <- krsa_read("data/DPLFC_MvsF_STK.txt") %>% filter(!SampleName %in% c("C1", "C2"))

```

## QC Initial Steps and Groups Assignments

We will perform a couple of quality control steps to deal with negative values in the data and adjust based on signal saturation (optional). Next, we will define a new column to represent the grouping. And then, we will extract end point signal values

```{r qcSteps, include=FALSE, cache=TRUE}
# qc processing
krsa_qc_steps(data,sat_qc = F) -> data

# Define sample groups
data %>% mutate(Group = `Comment 1`) -> data

# extract end level signal values @ all max exposure time (200ms)
krsa_extractEndPointMaxExp(data, chipType) -> data_pw_200

# extract end level signal values end level @ all exposure times
krsa_extractEndPoint(data, chipType) -> data_pw 


```

## QC Steps and Model Fitting

We will filter out peptides with low signals. In order to combine the values from different exposure times into a single value, a simple linear regression model of the *Medain_SigmBg* as a function of exposure time is fitted. The slope of of the model fit and $R^2$ are then used for quality control and samples comparison. The slope is also scaled by multiplying by 100 and log2 transformed (*Slope_Transformed*). We then filter out peptides with poor linear fit and references peptides.

```{r model, warning=F,include=FALSE, cache=TRUE}

# Filter out peptides with low signals
krsa_filter_lowPeps(data_pw_200, 5) -> ppPassAll

# Fit the linear model
# This will produce a list of data frames:
# scaled: the Slope_Transformed values (see above for more info on Slope_Transformed)
# normalized: the Slope_Transformed values but normalized by Chip/Barcode
# Grouped: The mean of Slope_Transformed values for all samples within a group
krsa_scaleModel(data_pw, ppPassAll) -> data_modeled
  
# Filter out peptides weak linear fit
krsa_filter_nonLinear(data_modeled$scaled, 0.9) -> ppPassR2

# Filter out reference peptides
krsa_filter_ref_pep(ppPassR2) -> new_pep


```

## Global Signal Intensity

For a global signal intensity across all samples/groups, few figures can be plotted based on the *Slope_Transformed* values.

### Global CV Plots

We will plot the coefficient of variation on both the normal and normalized fits. This will help us to identify groups with high variation that could be explained by sample outliers.

```{r cvPlot, echo=T,fig.height=8, fig.width=8, fig.align="center", cache=TRUE}

# Plot a CV figure using the modeled scaled data
krsa_cv_plot(data_modeled$scaled, ppPassR2)

```

### Global Violin Plots

We will plot violin figures to examine global signal differences between groups/samples.

```{r violinPlot, echo=T,fig.height=8, fig.width=8, fig.align="center", cache=TRUE}
# Plot a violin figure and facet by the (Group) variable
krsa_violin_plot(data_modeled$scaled, ppPassR2, "Group")

# Plot a violin figure and facet by the (Barcode) variable
krsa_violin_plot(data_modeled$scaled, ppPassR2, "Barcode")

```

### Global Heatmaps

The heatmap represent all the peptides present on the chip except the positive/internal controls and peptides that failed to pass QC. The heatmaps are scaled by row to highlight the peptide signal differences across the samples. A hierarchical unsupervised clustering is applied both on the peptides and the samples to potentially group similar signatures.

```{r heatmapPlot, echo=T,fig.height=8, fig.width=8, fig.align="center", cache=TRUE}

# Generates a heatmap using the modeled scaled data
krsa_heatmap(data_modeled$scaled, ppPassR2, scale = "row", cluster_col = F)


# Generates a heatmap using the modeled grouped data
krsa_heatmap_grouped(data_modeled$grouped, ppPassR2, scale = "none")


```

## Group Comparison

To compare between samples, a two-group comparison is performed. In this case, the two group comparisons are:

-   **Males vs Females**

The *Slope_Transforemed* ratio between each group, paired by chip, is calculated to the fold change. Based on the fold change, peptides that pass a certain fold change threshold are considered significant hits. Also, quality control steps applied in each comparison to filter out peptides that do not reach specific criteria:

-   The *Medain_SigmBg* at max exposure *200ms* must be above a certain value\
-   $R^2$ of the linear model fit must be above a threshold value

These *Filtering Parameters* (fold change threshold, QC criteria) can be modified to adjust the stringency of the analysis. The *Filtering Parameters* that are used for this analysis:

-   The *Medain_SigmBg* at max exposure *200ms* must be equal or above 5\
-   $R^2$ of the linear model fit must be above or equal 0.9\
-   Log fold change (LFC) cutoffs at (0.4,0.5,0.6)

```{r groupDiff,echo=T, fig.height=8,fig.width=7, cache=TRUE}

# Define Groups to be compared - Females as the "control"/"baseline"
comparisons <- list(Comp1 = c("M", "F"))

# This function will run both QC steps (krsa_filter_lowPeps, krsa_filter_nonLinear) and krsa_filter_ref_pep

krsa_quick_filter(data = data_pw_200, data2 = data_modeled$scaled,
    signal_threshold = 5, r2_threshold = 0.9,
    groups = comparisons$Comp1) -> pep_passed_qc

# This function calculates log2 fold change values between the defined groups
# The byChip argument lets you calculates the log2 fold change the results within each chip
krsa_group_diff(data_modeled$scaled, comparisons$Comp1, pep_passed_qc, byChip = F) -> diff_df

# Extract top peptides based on the LFC cutoff
krsa_get_diff(diff_df,LFC ,c(0.2,0.3,0.4)) %>% list("meanLFC" = .) -> sigPeps

# Combine the peptides hits in one list
sigPeps_total <- list(sigPeps) %>% unlist(recursive = F) %>%  unlist(recursive = F)


```

\newpage

### Males vs Females (Heatmap)

After applying the *Filtering Parameters* for this group comparison, only *`r length(sigPeps$meanLFC[["0.2"]])`*/141 peptides carried forward in the analysis (i.e. *`r length(sigPeps$meanLFC[["0.2"]])` hits*). Below are some figures to visualize the differences between these samples for considering these *hits*.

```{r heatmapInd,echo=T, fig.align="center", fig.height=6, fig.width=6, cache=TRUE}

# generates a heatmap using the selected groups and peptides
pdf("figures/dlpfc_heatmap.pdf", useDingbats = F, height = 15, width = 15)
krsa_heatmap(data_modeled$scaled, sigPeps$meanLFC[["0.2"]], groups = comparisons$Comp1, scale = "row", cluster_col = F)
dev.off()

```

\newpage

### Males vs Females (Violin Plot)

```{r violinIndPlot,echo=T, fig.align="center", fig.height=6, fig.width=8, cache=TRUE}
# generates a violin plot using the selected groups and peptides
krsa_violin_plot(data_modeled$scaled, sigPeps$meanLFC[["0.2"]], "Barcode", groups = comparisons$Comp1)



# generates grouped violin plot
pdf("figures/dlpfc_violin_plot.pdf", useDingbats = F, height = 15, width = 10)
krsa_violin_plot_grouped(data_modeled$scaled, sigPeps$meanLFC[["0.2"]], grp_comp = comparisons,
                   avg_line =  T, 
                   dots = T
                   )
dev.off()


```

\newpage

### Males vs Females (Waterfall Plot)

This waterfall represents the log2 fold changes between the two groups at each peptide.

```{r waterfall, echo=T, fig.align="center", fig.height=8,fig.width=6, cache=TRUE}
# generates a waterfall of the log2 fold change values for the selected peptide (top peptides)

pdf("figures/waterfall_plot.pdf", useDingbats = F, height = 15, width = 10)
krsa_waterfall(diff_df, 0.2, byChip = F)
dev.off()
```

\newpage

### Males vs Females (Curve Plot)

We generate curves plots per peptide using the last cycle data to visualize the linear fit model

```{r curvePlot, echo=T,fig.align="center", fig.height=8, fig.width=8, cache=TRUE}
# generates a curve plot representing the linear model fit for the selected peptide (top peptides)
krsa_curve_plot(data_pw, sigPeps$meanLFC$`0.2`, groups = comparisons$Comp1)


peps <- c("ACM4_456_468", "CFTR_730_742", "VASP_150_162")

krsa_curve_plot(data_pw, peps, groups = comparisons$Comp1, byGroup = F) -> p1

# to put in one column
p1$facet <- NULL

pdf("figures/cuvres_plot.pdf", useDingbats = F, height = 10, width = 8)
p1 + facet_wrap(~Peptide, ncol = 1, scales = "free_y")
dev.off()

```

### Males vs Females (Upstream Kinase Analysis)

The lab carefully curated and mapped the kinases that can act and phosphorylate each peptide present on the chip. This was achieved by using multiple sources including GPS 3.0, Kinexus Phosphonet, PhosphoELM and PhosphoSite Plus. Based on that association between peptides and kinases, a random sampling analysis is performed for these hits. The basic idea of *KRSA* is: For each iteration (*2000* iterations performed in this analysis), the same number of hits are randomly selected from the total 141/or 193 peptides present on the chip. Predicted kinases are then mapped to this sample list of peptides and number of kinases are determined. The kinase count from the actual hits and random sampling is then compared to determine the significance.

```{r krsa, echo=T, warning=F, message=FALSE, fig.align="center", fig.height=6, fig.width=6, cache=TRUE}


# load in chip coverage and kinase-substrate files OR upload your own files
chipCov <- KRSA_coverage_STK_PamChip_87102_v1
KRSA_file <- KRSA_Mapping_STK_PamChip_87102_v1

# run the KRSA function to do the random sampling analysis
krsa(sigPeps$meanLFC$`0.2`, return_count = T, seed = 123, itr = 2000) -> fin

# View the Z score table
kable(head(fin$KRSA_Table,25), digits = 3)

# to save file
fin$KRSA_Table %>% write_delim("acrossChip_KRSA_FullTable_0_2LFC.txt", delim = "\t")

# find top and bottom kinases
bothways <- c(pull(head(fin$KRSA_Table, 10), Kinase), pull(tail(fin$KRSA_Table, 10), Kinase))

# Use these kinase to generate histogram plots for each selected kinase
pdf("figures/dlpfc_histograms.pdf", useDingbats = F, height = 10, width = 10)
krsa_histogram_plot(fin$KRSA_Table, fin$count_mtx, bothways) +
  labs(x = "Mapped Hits", 
       y = "Cumulative Counts")
dev.off()


# For parallel computing, load the furrr package:
# opens multiple R sessions to run faster
plan(multisession)

# Run the KRSA function across the different sets of peptides using the furrr package for parallel computing
future_map(sigPeps_total, krsa) -> mutiple_krsa_outputs


# For none parallel computing:
# Run KRSA function across the different sets of peptides
#map(sigPeps_total, krsa) -> mutiple_krsa_outputs

# Tidy output
df <- data.frame(matrix(unlist(mutiple_krsa_outputs), ncol = max(lengths(mutiple_krsa_outputs)), byrow = TRUE))
df <- setNames(do.call(rbind.data.frame, mutiple_krsa_outputs), names(mutiple_krsa_outputs$meanLFC.0.2))

df %>% rownames_to_column("method") %>% select(Kinase, Z, method) %>% 
  mutate(method = str_extract(method, "\\w+\\.\\w+\\.\\w+")) %>% 
  mutate(method = gsub("(^\\w+)[\\.]", "\\1>", method)) %>% 
  mutate_if(is.numeric, round, 2) -> df

df %>% 
  pivot_wider(names_from = method, values_from = Z) -> df2
  
# Generates a table of the Z scores across the different sets of peptides
df2 %>%
  gt() %>% tab_spanner_delim(delim = ">")

# Creates an average Z score table using the across chip analysis
df %>% 
  filter(grepl("mean", method)) %>% 
  select(Kinase, Z, method) %>% group_by(Kinase) %>% mutate(AvgZ = mean(Z)) -> AvgZTable

#save file
AvgZTable %>% write_delim("acrossChip_KRSA_Table_multipleComp.txt", delim = "\t")


# Extract top kinases based on abs(Z) score
krsa_top_hits(AvgZTable, 2) -> kinases_hits
# krsa_top_hits(AvgZTable2, 1.75)
# krsa_top_hits(AvgZTable2, 1.5)

# Show the number of peptides per each set in atable
krsa_show_peptides(sigPeps_total)

```

\newpage

### Males vs Females (Z Scores Plot)

We will plot the individual and averaged Z scores using the across chip analyses.

```{r zscoresPlot, echo=T, warning=F, fig.align="center", fig.height=8,fig.width=6, cache=TRUE}

# Generates the Z scores waterfall plot
pdf("figures/dlpfc_szores.pdf", useDingbats = F, height = 15, width = 15)
krsa_zscores_plot(AvgZTable)
dev.off()

```

\newpage

### Males vs Females (Reverse KRSA Plot)

We will use the reverse KRSA plot function, to plot the log2 fold chnage values for all peptides mapped to kinase hits. This will help us examine the activity of the kinase

```{r revKRSAPlot, echo=T, warning=F, fig.align="center", fig.height=6, fig.width=6, cache=TRUE}

# plot the reverse KRSA figure for top kinases to determine their activity levels
krsa_reverse_krsa_plot(chipCov, diff_df, kinases_hits, 0.2, byChip = F)
```

\newpage

### Males vs Females (Coverage Plot)

To view the coverage of kinases across the full list of peptides on the chip, we will use the coverage plot function

```{r covPlot, echo=T, fig.align="center", fig.height=8,fig.width=6, cache=TRUE}

# generates a kinase covergae plot 
krsa_coverage_plot(chipCov, AvgZTable, chipType)

```

\newpage

### Males vs Females (Ball Model Network)

We will view the ball model network function, to generate a model representing the protein-protein interactions between kinases

```{r netPlot, echo=T, fig.align="center", fig.height=8,fig.width=8, message=FALSE, cache=TRUE}

# Plot the network ball model
pdf("figures/dplfc_network.pdf", useDingbats = F, height = 10, width = 10)
krsa_ball_model(kinases_hits, AvgZTable, 10, 3, 4.8)
dev.off()


```



```{r reading}


raw <- readxl::read_xlsx("data/Export_Tis100_brain_data_extended.xlsx", sheet = 4, col_names = F,
                         na = c("NA", "")
                         )


raw[2:16,5:ncol(raw)] -> valueInfo
dim(raw)
raw[18:159,] -> data
data <- data[, c(1,6:ncol(data))]

df2 <- data.frame(t(data[-1]), stringsAsFactors = F)
colnames(df2) <- data$...1
colnames(df2) <- make.unique(colnames(df2)) 

df3 <- data.frame(t(valueInfo[-1]), stringsAsFactors = F)
colnames(df3) <- valueInfo$...5


cbind(df3,df2) -> df4
dim(df4)

df4 %>% select(-ATP, -`Comment 11`, -`Sample concentration`, -`protein conc [mg/ml]`, 
               -Detection
               ) -> df4
dim(df4)
df4 %>% gather(11:152, key = "Peptide", value  = "Signal") -> tidydata
#glimpse(tidydata)

tidydata$Signal <- as.numeric(tidydata$Signal)

tidydata %>% dplyr::rename(SampleName = `Sample name`, 
                           Group = Grouping
                           ) -> tidydata



tidydata %>% dplyr::filter(`Braak stage Tau` == "1") %>% 
  select(SampleName, Array) %>% distinct() %>% 
  count(SampleName)



```

## Heatmap

```{r coh2_heatmap, echo=FALSE}
tidydata %>% mutate(SampleName2 = paste0(SampleName, "_", Array, "_", Barcode)) %>% 
  select(SampleName2, Gender, Barcode) %>% distinct(SampleName2, .keep_all = T) %>% 
  dplyr::rename(Chip = Barcode) %>% 
  column_to_rownames("SampleName2") -> levels_tbl 

tidydata %>% select(Peptide, Signal) %>% group_by(Peptide) %>% 
  summarise(sd = sd(Signal)) %>% filter(sd != 0) %>% 
  pull(Peptide) -> sd_peps

tidydata %>% dplyr::filter(`Braak stage Tau` == "1", Peptide %in% sd_peps) %>%
  ungroup() %>% 
  mutate(Signal = ifelse(Signal == 0, 0.1, Signal)) %>% 
  dplyr::group_by(SampleName,Peptide) %>% 
  dplyr::mutate(AvgSignal = EnvStats::geoMean(Signal, na.rm = T)) %>%
  dplyr::select(-Signal,-Array) %>% distinct(SampleName, Peptide, .keep_all = T) -> tidydata2


tidydata %>% 
  select(SampleName, Gender) %>% rename(Sex = Gender) %>% 
  mutate(Sex = factor(Sex, levels = c("M", "F"))) %>% 
  distinct(SampleName, .keep_all = T) %>% 
  column_to_rownames("SampleName") -> levels_tbl2 

tidydata %>% mutate(SampleName2 = paste0(SampleName, "_", Array, "_", Barcode)) %>%
  select(SampleName2, Peptide, Signal) %>% filter(Peptide %in% sd_peps) %>% 
  pivot_wider(names_from = SampleName2, values_from = Signal) -> DF

DF[rowSums(DF == 0) <= 10, ] %>% pull(Peptide) -> sd_peps_2



```


```{r, echo=FALSE}

library(factoextra)


new_my_data <- tidydata2 %>% 
  filter(Peptide %in% sd_peps_2) %>%
  mutate_at(c("Barcode", "SFactor10", "Braak stage Tau", "Age", "PMD"), as.numeric)

new_my_data %>% select(SampleName, Peptide, Barcode, Gender, AvgSignal, PMD, Age) %>%
  filter(Peptide %in% sd_peps_2)  -> new_my_data

new_my_data %>% mutate(
Gender = case_when(
  Gender == "M" ~ 1,
  Gender == "F" ~ 2,
  T ~ 3
), PMD = ifelse(is.na(PMD), 0, PMD)) %>% filter(Gender != 3) %>% 
  pivot_wider(names_from = Peptide, values_from = AvgSignal) -> new_my_data

new_my_data %>% column_to_rownames("SampleName") -> ad_pca

pca_res <- prcomp(ad_pca, center = T, scale. = T)


pdf("figures/pca_krsa_fin.pdf",useDingbats = F, width = 9, height = 8)

fviz_pca_biplot(pca_res, label = "var", 
                select.var = list(name = c("Age", "PMD", "Gender", "Barcode", "Braak stage Tau")),
                habillage=new_my_data$Gender,
                #addEllipses = T,
                col.var = "blue"
                )

dev.off()

pdf("figures/pca_comp_krsa_fin.pdf",useDingbats = F, width = 9, height = 8)
fviz_eig(pca_res, addlabels = TRUE, ylim = c(0, 60))
dev.off()


```

```{r upstream, echo=T, warning=F, fig.align="center", fig.height=8,fig.width=6, }


tidydata2 %>% 
  filter(Peptide %in% sd_peps_2, Peptide != "ART_025_CXGLRRWSLGGLRRWSL") %>%
  group_by(Gender, Peptide) %>% 
  summarise(mean = mean(AvgSignal)) %>% 
  pivot_wider(names_from = Gender, values_from = mean) %>% 
  mutate(LFC = M - F) %>% select(Peptide, LFC) -> ad_lfc_table


krsa_get_diff(ad_lfc_table,LFC ,c(0.2,0.3,0.4)) %>% list("meanLFC" = .) -> ad_peps

# Combine the peptides hits in one list
ad_sigPeps_total <- list(ad_peps) %>% unlist(recursive = F) %>%  unlist(recursive = F)

col_breaks2 <- c(seq(-4, -0.01,length=50),0,
          seq(0.01,4,length=50))

hmcol2 <- colorRampPalette(c("yellow", "white", "red"))(n = 100)


pdf("figures/Heatmap_MvsF_KRSA_AllConSamples_New.pdf", useDingbats = F, height = 15, width = 15)
tidydata2 %>% filter(Peptide %in% ad_peps$meanLFC$`0.2`, Peptide != "ART_025_CXGLRRWSLGGLRRWSL") %>% 
  select(SampleName, Peptide, AvgSignal) %>% 
  pivot_wider(names_from = SampleName, values_from = AvgSignal) %>%
  column_to_rownames("Peptide") %>% as.matrix() %>%
  pheatmap::pheatmap(annotation_col = levels_tbl2, 
                   
                     fontsize_col = 5,
                     fontsize_row = 5, 
                     scale = "row",
                     breaks = col_breaks2,
                    col = hmcol2,
                    clustering_method = "average",
                    cluster_cols = T, 
                    cluster_rows = T,
                    show_rownames = T, 
                    show_colnames = F
                     )
dev.off()


pdf("figures/hpc_violin_plot.pdf", useDingbats = F, height = 15, width = 10)
tidydata2 %>% select(-Group) %>% 
  rename(slope = AvgSignal, Group = Gender) %>% 
  krsa_violin_plot_grouped(ad_peps$meanLFC$`0.2`, grp_comp = list(Comp1 = c("M", "F")), 
                           groups = c("M", "F"),
                           lines = T,
                           dots = F,
                           avg_line = T
                           )
dev.off()


krsa(ad_peps$meanLFC$`0.2`, 
     map_file = KRSA_Mapping_STK_PamChip_87102_v1, 
     cov_file = KRSA_coverage_STK_PamChip_87102_v1) -> ad_krsa_output


ad_krsa_output %>% write_delim("acrossChip_KRSA_Table_0_2_AD.txt", delim = "\t")

future_map(ad_sigPeps_total, krsa, 
           map_file = KRSA_Mapping_STK_PamChip_87102_v1, 
           cov_file = KRSA_coverage_STK_PamChip_87102_v1) -> ad_mutiple_krsa_outputs

# clean up krsa output
df_ad <- data.frame(matrix(unlist(ad_mutiple_krsa_outputs), ncol = max(lengths(ad_mutiple_krsa_outputs)), byrow = TRUE))
df_ad <- setNames(do.call(rbind.data.frame, ad_mutiple_krsa_outputs), names(ad_mutiple_krsa_outputs$meanLFC.0.2))

df_ad %>% rownames_to_column("method") %>% select(Kinase, Z, method) %>% 
  mutate(method = str_extract(method, "\\w+\\.\\w+\\.\\w+")) %>% 
  mutate(method = gsub("(^\\w+)[\\.]", "\\1>", method)) %>% 
  mutate_if(is.numeric, round, 2) -> df_ad

df_ad %>% 
  pivot_wider(names_from = method, values_from = Z) -> df_ad2
  
# Generates a table of the Z scores across the different sets of peptides and just show top 10
df_ad2 %>% head(10) %>% 
  gt() %>% tab_spanner_delim(delim = ">")

# Creates an average Z score table using the across chip analysis
df_ad %>% 
  filter(grepl("mean", method)) %>% 
  select(Kinase, Z, method) %>% group_by(Kinase) %>% mutate(AvgZ = mean(Z)) -> AvgZTable_ad

#save file
AvgZTable_ad %>% write_delim("acrossChip_KRSA_Table_multipleComp_AD.txt", delim = "\t")


# Extract top kinases based on abs(Z) score
krsa_top_hits(AvgZTable_ad, 2) -> kinases_hits
# krsa_top_hits(AvgZTable2, 1.75)
# krsa_top_hits(AvgZTable2, 1.5)

# Show the number of peptides per each set in atable
krsa_show_peptides(ad_sigPeps_total)

pdf("figures/hpc_szores.pdf", useDingbats = F, height = 15, width = 15)
krsa_zscores_plot(AvgZTable_ad)
dev.off()
```

```{r}

DLPFC_hits <- read_delim("acrossChip_KRSA_Table_multipleComp.txt", delim = "\t")
HPC_hits <- read_delim("acrossChip_KRSA_Table_multipleComp_AD.txt", delim = "\t")

DLPFC_hits %>% filter(abs(AvgZ) >= 2) %>% pull(Kinase) %>% unique() -> DLPFC_hits_top_2
HPC_hits %>% filter(abs(AvgZ) >= 2) %>% pull(Kinase) %>% unique() -> HPC_hits_top_2

x2 <- list(`DLPFC`=DLPFC_hits_top_2 , `HPC`=HPC_hits_top_2
           )
pdf("figures/venn_diagram_2.pdf",useDingbats = F, width = 9, height = 8)
RAM::group.venn(x2,
                cat.cex = 1,
                lab.cex = 1,
                cat.pos = c(0,0),
                fill = c("red", "blue")
                )
dev.off()
  


```


```{r}

dplfc_tbl <- read_delim("acrossChip_KRSA_FullTable_0_2LFC.txt", delim = "\t")
hpc_tbl <- read_delim("acrossChip_KRSA_Table_0_2_AD.txt", delim = "\t")


dplfc_tbl %>% 
  head(10) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  gt() %>% 
  cols_align(align = "center") %>% 
  gtsave("figures/dlpfc_krsaTable.png")


hpc_tbl %>% 
  head(10) %>% 
  mutate_if(is.numeric, round, 2) %>% 
  gt() %>% 
  cols_align(align = "center") %>% 
  gtsave("figures/hpc_krsaTable.png")


```

#### Session Info

```{r}
installed.packages()[names(sessionInfo()$otherPkgs), "Version"]
```

