---
title: "KRSA and Enrichr"
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(KRSA)
library(knitr)
library(tidyverse)
```

# Using Enrichr and KRSA

You can perform gene set enrichment analysis using Enrichr by using either a set of PamChip peptide IDs or gene symbols.


# Using Peptide IDs

```{r, echo=T,out.width = "400px",out.width="450px", fig.align='center', cache=TRUE}

example_peptide_list <- c("ACM5_494_506", "ADDB_696_708", "ADRB2_338_350", "ANXA1_209_221")

enrichr_results <- krsa_enrichr(peptides = example_peptide_list)


head(enrichr_results, 10)


```



## Using Gene Symbols

Alternatively, the input coould be gene symbols instead of peptide ids: 


```{r, echo=T,out.width = "400px",out.width="450px", fig.align='center', cache=TRUE}


enrichr_results_genes <- krsa_enrichr(genes = c("AKT1", "AKT2", "AKTe"))


head(enrichr_results_genes, 10)


```


# Visualization  

The results could be plotted using the *krsa_enrichr_plot* function: 

```{r plot, echo=T, fig.width=10, fig.height=8, fig.align="center", cache=TRUE}

krsa_enrichr_plot(enrichr_results)


```


Showing only top 5 terms per library: 
`
```{r plot2, echo=T, fig.width=10, fig.height=8, fig.align="center", cache=TRUE}

krsa_enrichr_plot(enrichr_results, terms_to_plot = 5)


```
